Respected Dr. Vincenzo Loia and Editor(s) and reviewers, 

Thank you for your valuable and positive review comments for the Manuscript entitled “WALE: A Weighted Adaptive Location Estimation Algorithm”. We are delighted that you are interested in the paper and appreciate your comments and valuable suggestions. 

We have carefully reviewed the comments and revised the manuscript as advised. Our responses to the comments have been addressed  and we have taken efforts to address the reviewer concerns as best as possible. 

We hope the revised version is now suitable for publication and look forward to hear from you in due course.

RESPONSES FOR THE COMMENTS:

The primary comments regarding the paper have been with respect to the structuring of the paper and description of algorithm. There were also concerns about grammatical errors. 

>> We have reworked the structure of the paper and enhanced the writing in certain sections so that the clarity is improved specifically in Sections 3 and 4. Examples and figures have been added to improve readability. Additionally, we have re-structured our paragraphs in order to convey meanings more accurately and maintain a certain flow of the general idea. We have added references in multiple places throughout the manuscript and explained methods and keywords better.  We regret the presence of grammatical errors and typos, and have made sure to address this in the revised version. We have fixed all the grammatical and semantical errors, reworded sentences and cropped images better. 

Some of the specific changes in addition to the above are mentioned below.

1. "I recommend to avoid repetitive "we wil describe.... " since makes it difficult to follow in some points the scientific approach."

>> We have removed all the repetitive phrases that we have used in the manuscript. 

2. The introduction need to provide more relevant references.

>> References have been added wherever relevant in the introduction.


